### 2019-12-17 images/flow.tex

\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
	base/.style = {draw, on chain, on grid, align=center, minimum height=4ex},
	Docs/.style = {base, fill=blue!30},
	screen/.style = {base, fill=orange!15},
	form/.style = {on chain, on grid, align=center, minimum height=4ex, fill=white},
    computer/.style = {base, fill=green!30},
    decision/.style={base, diamond, aspect=2.5, fill=red!30,text width=5em},
	process/.style = {base, minimum width=2.5cm, fill=orange!15,
                           font=\ttfamily},                       
    coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
	norm/.style={->, draw, black},  
	multidoc/.style={
		base,
		shape=tape,
		tape bend top=none,
		fill=white,
		double copy shadow,
		fill=blue!30
	},
}
\begin{document}    
% Drawing part, node distance is 1.5 cm and every node
% is prefilled with white background

@@

  \node (sample)  [screen, join]  {Screen random documents};
  \node (model) [computer, join, left=of sample]  {Train model,\\ predict relevance};
  \node (screenrel)  [screen, below of =sample]  {Screen most \\ relevant documents};
  \node (stopscreen) [decision, join] {Irrelevant?};

@@

  \node (recall) [decision, join] {Recall $>$ threshold?};

    	\node (e1) [form, right=of stopscreen, xshift=-15mm] { $p < 1-\frac{\alpha}{2}$ };

@@

  \node (rform) [form, right=of recall, xshift=-15mm] { $p < 1-\alpha $ };

  \node (reldocs) [multidoc, below of=recall, xshift=20mm, yshift=-8mm]  {Relevant documents};
  \node (irreldocs) [multidoc, fill=blue!5, below of=recall, xshift=-20mm, yshift=-8mm]  {Irrelevant documents};
  %\node

@@

 \path (stopscreen.west) to node [very near start, yshift=1em] {$n$} (c1);

@@

  \path (recall.west) to node [very near start, yshift=1em] {$n$} (c3);

@@

 \draw [o->,norm] (recall.south) -- (reldocs);
 \draw [o->,norm] (recall.south) -- (irreldocs);

>>>>

\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
	base/.style = {draw, on chain, on grid, align=center, minimum height=4ex},
	Docs/.style = {base, fill=blue!30},
	screen/.style = {base, fill=orange!15},
	form/.style = {on chain, on grid, align=center, minimum height=4ex, fill=white},
    computer/.style = {base, fill=green!30},
    decision/.style={base, diamond, aspect=2.5, fill=red!30,text width=5em},
	process/.style = {base, minimum width=2.5cm, fill=orange!15,
                           font=\ttfamily},                       
    coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
	norm/.style={->, draw, black},  
	multidoc/.style={
		base,
		shape=tape,
		tape bend top=none,
		fill=white,
		double copy shadow,
		fill=blue!30
	},
	end/.style={
		base,
		shape=ellipse,
		fill={rgb:red,1;green,2;blue,5},
		text=white
	}
}
\begin{document}    
% Drawing part, node distance is 1.5 cm and every node
% is prefilled with white background

@@

  \node (sample)  [screen, join]  {Screen random documents};
  \node (model) [computer, join, left=of sample]  {Train model,\\ predict relevance};
  \node (screenrel)  [screen, below of =sample]  {Screen most \\ relevant documents};
  \node (stopscreen) [decision, join] {Recall unlikely $<$ threshold?};

@@

  \node (recall) [decision, join] {Recall unlikely $<$ threshold?};

    	\node (e1) [form, right=of stopscreen, xshift=-10mm] { $p < 1-\frac{\alpha}{2}$ };

@@

  \node (rform) [form, right=of recall, xshift=-10mm] { $p < 1-\alpha $ };

  \node (stop) [end, below of=recall, yshift=-10mm] {Stop};

  \node (reldocs) [multidoc, below of=stop, xshift=20mm, yshift=-8mm]  {Relevant documents};
  \node (irreldocs) [multidoc, fill=blue!5, below of=stop, xshift=-20mm, yshift=-8mm]  {Irrelevant documents};
  %\node

@@

 \path (stopscreen.west) to node [very near start, yshift=1em] {$no$} (c1);

@@

  \path (recall.west) to node [very near start, yshift=1em] {$no$} (c3);

    \path (stopscreen.south) to node [very near start, yshift=-0.5em, xshift=1em] {$yes$} (screenr2.north);

    \path (recall.south) to node [very near start, yshift=-0.5em, xshift=1em] {$yes$} (stop.north);

@@

 \draw [o->,norm] (recall.south) -- (stop);

 \draw [o->,norm] (stop.south) -- (reldocs);
 \draw [o->,norm] (stop.south) -- (irreldocs);
